Reflections from reproductions

### 2024-08-15 pages/reflections.qmd
feat(reflections): started on reflections, with 2 alternative versions for layout

---
title: "Reflections from reproductions"
---

TODO: Table with reflections from each study

>>>>

---
title: "Reflections from reproductions"
bibliography: ../references.bib
---

The table below outlines the factors that helped facilitate reproductions, or that would have been helpful (i.e. their absence was a barrier to the reproduction).

To present this concisely, each facilitator identified has been listed in a table, and I have evaluated for each study whether this was fully met (✅), partially met (🟡), not met (❌) or not applicable (N/A).

# Version 1

## Environment

::: {.callout-note appearance="minimal" collapse=true}

## List required packages

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ |

@shoaib_simulation_2021: Became a time-consuming issue as it took a while to identify a dependency that was needed for the code to work (`greenlet`), and a while longer to realise I had installed another package when the package I needed was in base (`statistics`).

:::

::: {.callout-note appearance="minimal" collapse=true}

## Provide versions

| S | H | L | K | A | J |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ |

* In one study (@shoaib_simulation_2021) I had to backdate the package versions as the didn't work with the latest
* @huang_optimizing_2019 -
* @lim_staff_2020 -
* @kim_modelling_2021 -
* @anagnostou_facs-charm_2022 -
* @johnson_cost_2021

:::

## Running model programmatically

::: {.callout-note appearance="minimal" collapse=true}

## A

:::

# Version 2

Key:

* **S:** @shoaib_simulation_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-shoaib-2022/evaluation/reflections.html" target="_blank">link to reflections</a>
* **H:** @huang_optimizing_2019  - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-huang-2019/evaluation/reflections.html" target="_blank">link to reflections</a>
* **L:** @lim_staff_2020 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-lim-2020/evaluation/reflections.html" target="_blank">link to reflections</a>
* **K:** @kim_modelling_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-kim-2021/evaluation/reflections.html" target="_blank">link to reflections</a>
* **A:** @anagnostou_facs-charm_2022 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-anagnostou-2022/evaluation/reflections.html" target="_blank">link to reflections</a>
* **J:** @johnson_cost_2021 - <a href="https://pythonhealthdatascience.github.io/stars-reproduce-johnson-2021/evaluation/reflections.html" target="_blank">link to reflections</a>

| Facilitator | S | H | L | K | A | J |
| - | - | - | - | - | - | - |
| **Environment** |
| List required packages | ❌ |
| Provide versions | ❌ |
| **Running model programmatically** |
| |
| **Run time** |
| |
| **Parameters, scenarios and outputs** |
| All the required outputs are calculated | ❌ |
| **Output format** |
| Saves output to a file | ✅ |
| Easy to figure out how to use output table/s to create tables/figures | ❌ |
| **Seeds** |
| |
| **Code to produce article results** |
| Provide code to process results into tables | ❌ |
| Provide code to process results into figures | ❌ |
| Provide code to calculate results mentioned in the text (but no in tables/figures) | ❌ |
: {tbl-colwidths="[70, 5, 5, 5, 5, 5, 5]"}

\

## Extra notes

**Environment: List required packages**

@shoaib_simulation_2021: Became a time-consuming issue as it took a while to identify a dependency that was needed for the code to work (greenlet), and a while longer to realise I had installed another package when the package I needed was in base (statistics)

**Environment: Versions**

* In one study (@shoaib_simulation_2021) I had to backdate the package versions as the didn't work with the latest
* @huang_optimizing_2019 -
* @lim_staff_2020 -
* @kim_modelling_2021 -
* @anagnostou_facs-charm_2022 -
* @johnson_cost_2021

**Output format: Easy to figure out how to use output table/s to create tables/figures**

* For @shoaib_simulation_2021, there were two alternative results spreadsheets with some duplicate metrics but sometimes differing results between them, which made it a bit confusing to work out what to use

## References
